---
title: "EDS 123: An optional course template"
description: "Some byline about this class"
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(kableExtra)
# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages

```

## MEDS distill template

This is an optional [distill](https://rstudio.github.io/distill/) template for MEDS teachers who want to create a website for their courses. It is not required. 

A distill website allows you to create a streamlined, robust site with minimal infrastructure working just in R Markdown. 

## Adding new pages

New pages can be added by creating a new .Rmd for each new page on your site in the project root. The html will be rendered and saved in the /docs folder when you **Build website**. Then, add the new page information (text and html) to the navbar section of the _site.yml file.

### Don't work in the /docs folder

All files you want added to your site should be automatically sent to /docs when you build the site. Manually update things in the /docs folder at your own risk. 

## Some aesthetics for this template

### Tables 

With `kable()`:

```{r}
head(mtcars) %>% 
  kable() %>% 
  kable_styling(full_width = FALSE)
```

### Code

```{r, echo = TRUE, eval = FALSE}
ggplot(data = mtcars, aes(x = wt, y = mpg)) +
  geom_point() +
  labs(x = "Car weight",
       y = "Gas mileage")
```

